On Adding Pattern Matching to Haskell-based Deeply Embedded Domain Specific Languages

### 2020-11-17 paper/paper.tex
Add 'construct' implementations
formatting

\begin{lstlisting}
instance (ERep a, ERep b) => ERep (Either a b) where
  type ERepTy (Either a b) = Either a b

  rep (Left x)  = LeftExp (rep x)
  rep (Right y) = RightExp (rep y)
  unrep' = id
  rep'   = id

instance (ERep a, ERep b) => ERep (a, b) where
  type ERepTy (a, b) = (a, b)

  rep (x, y) = PairExp (rep x) (rep y)
  unrep' = id
  rep'   = id
\end{lstlisting}

>>>>

\begin{lstlisting}
instance (ERep a, ERep b) => ERep (Either a b) where
  type ERepTy (Either a b) = Either a b
  construct (Left x)  = LeftExp (rep x)
  construct (Right y) = RightExp (rep y)
  rep (Left x)  = LeftExp (rep x)
  rep (Right y) = RightExp (rep y)
  unrep' = id
  rep'   = id

instance (ERep a, ERep b) => ERep (a, b) where
  type ERepTy (a, b) = (a, b)
  construct (x, y) = PairExp (rep x) (rep y)
  rep (x, y) = PairExp (rep x) (rep y)
  unrep' = id
  rep'   = id
\end{lstlisting}
